Box

### 2021-10-08 MS/box.Rmd
Final fixes to send out. Added Patrice's paper

Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation, or as we call it, the acclimation response ratio (*ARR*). *ARR* can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:

>>>>

Let's start with a real example that comparative physiologists can easily relate with, the slope of responses to temperature acclimation, or as we call it, the acclimation response ratio (*ARR*) [@Pottier2021]. *ARR* can be defined as a slope for acclimated physiological responses at two different temperature points, defined as:
